The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-05-06 albatros_paper.tex
Changes to front and backend electronics section (some previous text left in for reference but commented out)

\subsection{Front-end active balun}
\textcolor{red}{\bf Tankiso, Eamon, Jeff?} \\
All the front end components were incorporated for in a double sided
printed circuit board (PCB) as shown in \autoref{Fig:Balun} and the
block diagram is shown in \autoref{Fig:Balun Schematic}. The
Monolithic Microwave Integrated Circuits (MMICs) is the used design
for the PCB. One side of the PCB is populated with components and the
other side is a solid copper ground plane aperiodically stitched to
the grounded copper on the side populated with components. The
receiver system is made up of the active balun, filter and the gain
stage that connects to the \SI{100}{\metre} coaxial cable which is
connected to the back end \cite{2012PASP..124.1090H}.

@@

@@

The back-end readout electronics are housed in a Faraday cage that is
located $\sim 100$~m away from the antennas to reduce potential
contamination from self-generated RFI.  Each of the four antenna
signals is passed to a second-stage electronics chain consisting of a
bias tee (Minicircuits ZFBT-4R2GW-FT+), amplifier (Minicircuits
ZX60-V63+), and a pair of high- and low-pass filters (Minicircuits
ZFHP-1R2+ and SLP-90+) that band limit the signal to
1.2--\SI{81}{MHz}.  A Smart Network ADC Processor (SNAP) board
digitizes the RF signals at 250~Msamp/s and calculates a full
cross-correlation of the four inputs, producing four auto- and six
cross-spectra as outputs.  \textcolor{red}{\bf finish merging text
  below into the above paragraph}

@@

\textbf{SNAP Board} - The SNAP board used is specified by Xilinx
Inc. \footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}. The
SNAP board samples the signals it receives by 250 Msampl/s using
internal ADCs where the signal of the clock is from the Valon 5007
frerquency synthesizer module. This creates a frequency range between
\SI{0}{MHz} - \SI{125}{MHz} which contains 2048 channels. A SNAP board
interacts with a raspberry pi and that is where the data is saved.
\textcolor{red}{\bf include text about firmware}

>>>>

\subsection{Front-end active balun}
\textcolor{red}{\bf Tankiso, Eamon, Jeff?} \\

The LWA active-balun front-end electronics (FEE) circuit uses  a MiniCircuits GALI-74+ MMIC to amplify each dipole leg against ground, presenting each leg with a 50$\ohm$ impedance and providing a nominal gain of 25dB. The two GALI-74+ outputs are differenced using a passive {180\degree} hybrid coupler. The coupler output is filtered by a $\sim$150MHz lowpass, and receives an additional 12dB of gain from a MiniCircuits GALI-6+ MMIC. This last amplifier drives the output signal onto a $\sim$100m 50$\ohm$ coaxial cable. Thus, neglecting mismatch loss between the dipoles (electrically small in the frequency range of interest) and the 100{\ohm} input impedance, as well as the hybrid insertion loss ($<$1dB), the front-end electronics provide a gain of $\sim$37dB \cite{2012PASP..124.1090H}.

Each FEE circuit is powered by 16V, fed on the coax through a bias tee.

% EE citing the noise figure of the GALI-74+ is particulary misleading because of the large mismatch loss, which directly scales up the noise figure in the HF band.

\iffalse

All the front end components were incorporated for in a double sided
printed circuit board (PCB) as shown in \autoref{Fig:Balun} and the
block diagram is shown in \autoref{Fig:Balun Schematic}. The
Monolithic Microwave Integrated Circuits (MMICs) is the used design
for the PCB. One side of the PCB is populated with components and the
other side is a solid copper ground plane aperiodically stitched to
the grounded copper on the side populated with components. The
receiver system is made up of the active balun, filter and the gain
stage that connects to the \SI{100}{\metre} coaxial cable which is
connected to the back end \cite{2012PASP..124.1090H}.

@@

\fi

@@

The back-end readout electronics are housed in a Faraday cage that is
located $\sim$100m away from the antennas to mitigate possible
self-generated RFI.  Each of the four antenna
signals is passed to a second-stage electronics chain consisting of 
% EE bias tee is already described; it isn't really part of the signal chain since it doesn't do much of anything
%a bias tee (Minicircuits ZFBT-4R2GW-FT+), 
an
amplifier (Minicircuits
ZX60-V63+), and a pair of high- and low-pass filters (Minicircuits
ZFHP-1R2+ and SLP-90+) that together  bandlimit the signal to
1.2--\SI{81}{MHz}.  The amplifier has a nominal gain of 20dB, and the HPF and LPF contribute nominal insertion losses of 0.2dB and 0.14dB respectively.

A Xilinx Kintex\footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html} based Smart Network ADC Processor (SNAP) board (\textcolor{red}{\bf citation for SNAP board?}), 
clocked by a Valon 5007 frequency synthesizer module,
digitizes the RF signals at 250~Msamp/s. It calculates a full
cross-correlation of the four inputs, producing four auto- and six
cross-spectra as outputs, over 2048 channels spanning the frequency range 
\SI{0}{MHz} - \SI{125}{MHz}. 
(\textcolor{red}{\bf details about SNAP board frequency transform?})
The SNAP board sends its output data via ethernet to a Raspberry Pi (\textcolor{red}{\bf version? citation?}), which saves it to a hard drive.

\iffalse

\textcolor{red}{\bf finish merging text
  below into the above paragraph}

@@

\textbf{SNAP Board} - The SNAP board used is specified by Xilinx
Inc. \footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}. 
% EE it's unclear what this means. The reference is to the Kintex FPGA family, which says nothing about the SNAP board
The
SNAP board samples the signals it receives by 250 Msampl/s using
internal ADCs where the signal of the clock is from the Valon 5007
frerquency synthesizer module. This creates a frequency range between
\SI{0}{MHz} - \SI{125}{MHz} which contains 2048 channels. A SNAP board
interacts with a raspberry pi and that is where the data is saved.
\textcolor{red}{\bf include text about firmware}

\fi
